Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-23 paper/main.tex
concat tables of AV & AO events; adjust references to table

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (Tab.~\ref{tab:av-events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at their first occurence in a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
katz1991film, mascelli1998five}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

@@

    movie.

@@

    % negative control Tab.~\ref{tab:ao-events}.

@@

\label{tab:av-events}

@@

@@

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly available annotation
of its speech content \citep{hausler2021studyforrest} by classifying
concrete and countable nouns that the narrator uses to describe the movie's absent visual content.
% annotation procedure
An initial annotation was performed by one individual,
% corrections
and minor corrections were applied after comparing with a second categorization
done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, their inclusion criteria, and examples
can be seen in Table~\ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{groom}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{groom};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (Tab.~\ref{tab:ao-events}).
These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[tbp]
    \caption{Categories and criteria to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (Tab.~\ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{Category} & \textbf{Criteria} & \textbf{Examples} \\
\midrule
\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{groom} & rooms \& locales, or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% AD regressors
    \caption{Overview of annotated stimulus features of the audio-description.
    the segments that were used for the eight sessions of fMRI scanning.
    Some of the annotation's original categories (female, females, fname; male,
    % For a description of the five control conditions for movie cuts see
    % Tab.~\ref{tab:av-events}.
\label{tab:ao-events}
\begin{tabular}{lp{3.8cm}lllllllll}
\toprule \textbf{Label} & \textbf{Description} & \textbf{All} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\

@@

@@

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; Tab.~\ref{tab:ao-events} for a
        description) and audio-visual movie (red; Tab.~\ref{tab:av-events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
      }
\label{fig:reg-corr}
\end{figure*}

% AV design matrix
The design matrices of the first-level time-series GLM analysis comprised the
regressors for the stimulus features listed in Tables~\ref{tab:av-events} and
\ref{tab:ao-events} for the movie and audio-description stimulus, respectively.
% AD regressors in AV
Additionally, the design for the movie stimulus also contained the
regressors based on nouns used by the audio-description's narrator to indicate
a switch to another setting (categories \texttt{se\_new} and \texttt{se\_old}),
in order to be able to implement cross-modal control contrasts.
% AV regressors in AV
Likewise, the audio-description design matrix included movie cut related regressors
listed Table~\ref{tab:av-events} (excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of
\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:ao-events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to compensate for
regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimated (translation and rotation)
were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

>>>>

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (Tab.~\ref{tab:events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at their first occurence in a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
katz1991film, mascelli1998five}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

@@

    movie and the audio-description.
    Some of the noun categories (female, females, fname; male,

@@

    % negative control Tab.~\ref{tab:events}.

@@

\label{tab:events}

@@

\multicolumn{3}{l}{\textit{Movie stimulus}}\\

@@

@@

\multicolumn{3}{l}{\textit{Audio-description stimulus}}\\

@@

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly available annotation
of its speech content \citep{hausler2021studyforrest} by classifying
concrete and countable nouns that the narrator uses to describe the movie's absent visual content.
% annotation procedure
An initial annotation was performed by one individual,
% corrections
and minor corrections were applied after comparing with a second categorization
done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, their inclusion criteria, and examples
can be seen in Table~\ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{groom}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{groom};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (Tab.~\ref{tab:events}).
These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[tbp]
    \caption{Categories and criteria to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (Tab.~\ref{tab:events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{Category} & \textbf{Criteria} & \textbf{Examples} \\
\midrule
\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{groom} & rooms \& locales, or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; Tab.~\ref{tab:events} for a
        description) and audio-visual movie (red; Tab.~\ref{tab:events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
      }
\label{fig:reg-corr}
\end{figure*}

% AV design matrix
The design matrices of the first-level time-series GLM analysis comprised the
regressors for the stimulus features listed in Tables~\ref{tab:events} and
\ref{tab:events} for the movie and audio-description stimulus, respectively.
% AD regressors in AV
Additionally, the design for the movie stimulus also contained the
regressors based on nouns used by the audio-description's narrator to indicate
a switch to another setting (categories \texttt{se\_new} and \texttt{se\_old}),
in order to be able to implement cross-modal control contrasts.
% AV regressors in AV
Likewise, the audio-description design matrix included movie cut related regressors
listed Table~\ref{tab:events} (excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of
\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to compensate for
regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimated (translation and rotation)
were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.
